---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HCL-32 psychometric properties

<!-- badges: start -->
[![R-CMD-check](https://github.com/brunomontezano/HCLpsychometrics/workflows/R-CMD-check/badge.svg)](https://github.com/brunomontezano/HCLpsychometrics/actions)
<!-- badges: end -->

The objective of `HCLpsychometrics` is to provide functions to perform the analyzes used in a study on the factor structure of the HCL-32 instrument in a population sample. The package has functions for executing routines for confirmatory factor analysis and Cronbach's alpha
coefficient estimation. 

#### Note

This repository is not intended to be used by others. It is a package aggregating several tools used to replicate the specific analysis of an article.

## Installation

The current version can be installed from
[GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("brunomontezano/HCLpsychometrics")
```

## Examples

### Confirmatory factor analysis

```{r}
library(HCLpsychometrics)

# First, the models to be tested are created
created_models <- create_models()

# Then, we can fit these models on given dataset
# that contains yX as variable names, X being numbers from 1 to 32
fitted_models <- fit_models(
  data = hcl,
  models = created_models
)

# Finally, I could for example, summarize the parameters
# (In this case, I just printed the first 3 rows to save space)
summarize_parameters(
  fits = fitted_models
  ) %>% purrr::map(head, 3)
```

## Cronbach's alpha

```{r}
# The alpha_authors_model function can be used to calculate Cronbach's
# alpha based on the author's model in the input dataset
HCLpsychometrics::alpha_authors_model(hcl)
```

